Digital History in Finland, 1488-1828

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
ok

Aatehistoria ja digitaalisten  aineistojen mahdollisuudet ([Tolonen & Lahti (2015)](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/)). Citing with URL `r citep("http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet")`

@@

We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)). Citing with DOI: `r citep("10.18352/lq.10112")`

@@

### Dependencies

>>>>

Aatehistoria ja digitaalisten aineistojen mahdollisuudet ([Tolonen &
Lahti (2015) - add to
bib](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/)).

@@

We have prepared open data analytical ecosystem for in-depth analysis
of such data collections `r citep("10.18352/lq.10112")`.

@@
